Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-07-15 paper/manuscript.tex

@@

Although the Zwanzig equation is formally correct (as long as the two states considered sample the same phase space volume, which is true for standard molecular models), it has some very important numerical issues that mean that it often performs badly for standard free energy calculations, even for small molecules~\cite{shirts2005comparison,lu2003appropriate}.  One can show that if the standard deviation of the difference $\Delta U(\vec{q}) = U_1(vec{q})-U_2(\vec{q})$ over all sampled $\vec{q}$ is large (which in this case, means only several times $k_BT)$, then very few samples contribute to the average, and the answer will be both biased and extremely noisy~\cite{lelievre2010free}. Essentially, the method is dominated by contributions of rare snapshots\cite{jarzynski2006rare, wu2005phasespaceb, wu2005phasespacec}. There are a number of applications where this expression is nevertheless useful, but those usually involve investigating the dependence of the free energy on small changes in parameters, not changing molecules or even single atoms in molecules~\cite{xx}
\paragraph{The Bennett Acceptance Ratio (BAR)}
If we have the differences in the potential energy sampled from the distribution defined by $U_0$ to the state defined by $U_1$, and we also have the differences in potential energies from the distribution sampled by $U_1$ to the state defined by $U_0$, we can obtain a significantly improved estimate of the
free energy difference compared to that obtained by EXP. 
This estimate was first derived by Bennett and is hence generally called the Bennett Acceptance Ratio (BAR).  It is solved by finding the reduced free energy $f_{ij}$ that satisfied the following implicit equation:
 \sum_{i=1}^{n_i} \frac{1}{1 + \exp[\ln(\frac{n_i}{n_j}) + u_{ij}(\vec{q}) - f_{ij})
 ]} \nonumber \\
 =\sum_{i=1}^{n_j} \frac{1}{1 + \exp[\ln(\frac{n_i}{n_j}) - U_{ij}(\vec{q}) + f_ij)]},
where $n_i$ and $n_j$ are the number of samples from each state. We
will refer to this method as BAR. More recent derivations show that this formula is the maximum likelihood estimate of the free energy difference given sets of samples from the two states~\cite{bennett1976efficient,shirts2003equilibriuma}.

Many studies have demonstrated both the theoretical and practical superiority of BAR over EXP in molecular
simulations~\cite{shirts2005comparison,lu2003appropriate}, and BAR converges to EXP in the limit that all samples are from a single state~\cite{bennett1976efficient,bennett1976efficient,shirts2003equilibriuma}. BAR also requires significantly less overlap between the configurational space of each state to converge than EXP, though some overlap must still exist.

@@

\paragraph{Thermodynamic integration (TI)}
By taking the derivative of the free energy with respect to the
variable $\vec{\lambda}$, we find that:
\begin{equation}
\frac{df}{d\vec{\lambda}} = \frac{d}{d\vec{\lambda}} \left[-\ln \int \frac{\exp{-u(\vec{\lambda},\vec{q})}}{Q(\vec{\lambda})} d\vec{q}\right] = \expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}\
}_{\vec{\lambda}} 
And than we can then numerically integrate $df/d\vec{\lambda}$ over an alchemical transformation, using a range of different well-established techniques, to obtain:
\begin{equation}
\Delta f    = \int_{0}^{1} \expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}}_{\vec{\lambda}}  d\vec{\lambda}    
This approach to calculating the free energy is called thermodynamic integration (TI). Averaging over $\expect{\frac{du}{d\vec{\lambda}}}$ requires fewer uncorrelated samples to reach a given level of relative error
than averaging $e^{-u(\vec{q})}$, as the range is usually narrower with a more Gaussian distribution. Rather than being limited by overlap, as in the case of BAR and MBAR (see below), we are instead limited by the bias in the numerical quadrature, which must be minimized sufficiently to be beneath the level of statistical noise.
Various numerical integration schemes are possible, but the trapezoid
rule provides a simple and robust scheme.  All types of numerical integration can be written as:
\[ \Delta f \approx \sum_{k=1}^{K} w_k
\expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}}_{k} \] where the weights $w_k$ correspond to a particular choice of numerical integration.
Researchers have tried a large number of different integration schemes~\cite{resat1993studies,jorge2010effect,shyu2009reducing}. However, many other integration choices require specific choices of $\vec{\lambda}$ to minimize bias, which makes them unsuitable when the intermediates
have widely-varying levels of uncertainty. For example, integrating a cubic spline interpolation provided negligible benefits~\cite{paliwal2011benchmark}. For starting researchers, we therefore recommend a simple trapezoid rule scheme, as it allows for maximal flexibility in which values of $\vec{\lambda}$ are simulated.  Because fitting to higher order polynomials can have numerical instabilities for some energy functions, and because alternate functional forms might only be appropriate with some types of transformations, expertise and experience is required to perform such numerical integration modifications. In practice, adding 2-3 more intermediate states is typically sufficient to match the performance of these more complicated numerical quadrature schemes.

@@

\paragraph{The multistate Bennett acceptance ratio (MBAR)}
One can generalize Bennett's logic from two states to multiple states to obtain a free energy estimator that uses energy differences between all intermediate states. MBAR gives a system of implicit equations for the free energies $f_i$:
\begin{equation}
f_i = - \ln \sum_{n=1}^{N} \frac{\exp(-u_i(\vec{q}_n))}{\sum_{k=1}^K N_k \exp(f_k-u_k(\vec{q}_n))}
where there are $N_k$ samples from each of $K$ states, with $\sum_k N_k=N$ the total number of samples. Thus, we need to evaluate the energy function $U_i$ for all samples obtained at all states in the transformation. The equations can be solved by a number of different standard routines. We note that there are only $K-1$ independent equations, so only K-1 of the free energies are independent variables, and one of the $f_i$ must be specified (usually, without loss of generality, setting it to zero).

@@

\paragraph{Recommendations}
\item We recommend MBAR if all energy differences are available. It is probably the lowest variance free energy estimate given samples from multiple states.
\item BAR is essentially just as good as MBAR for highly optimized $\vec{\lambda}$ intermediates. Specifically, if the $\vec{\lambda}$s are chosen such that intermediate states have moderate overlap with their neighbors (i.e. between $i$ and $i+1$ and between $i$ and $i-1$, they will \textit{not} have significant overlap with their next nearest neighbors $i+2$ and $i-2$. Thus MBAR does not actually get significant information from these energy differences, so one might as well not even calculate them, and just perform BAR between nearest neighbors.~\cite{paliwal2011benchmark} 
\item TI usually gives similar values as MBAR implemented with sufficient numbers of intermediates, but quadrature errors are hard to estimate beforehand.~\cite{paliwal2011benchmark}
\item WHAM is an approximation to MBAR, and there are no compelling reasons it should be used. 
\item Other variants, especially ones that adaptively determine the free energies can be  useful in certain circumstances but beyond the scope of a Best Practices article.
\subsection{Uncertainty estimation}
\label{subsec:uncertainty}
It is important to consider the variation in your computed free energies from your equilibrium simulations, in order  to  obtain an estimate of  uncertainty of the obtained value for the free energies of interest. A recent best practices paper by Grossfield et. al~\cite{grossfield2018best} provides substantial detail on how to estimate uncertainties from molecular simulations and is a good starting point for this topic. 
In general the quantification of different error metrics depends on both data generation and analysis methods  used from the ones discussed above.

The computation of free energies using TI (section~\ref{subsec:estimators}) is straightforward and the trapezoidal rule is often recommended since it allows unequal spacing of $\vec{\lambda}$ states, which is required to minimize the variance in the free energy estimate, but in principle any good numerical integration method can be used. 
The determination of regions of high curvature when estimating the integral is helpful to determine regions of phase space where more sampling and/or more $\vec{\lambda}$ states are necessary to obtain the best approximation of the integral. Generally a plot of $\vec{\lambda}$ with respect to the gradients at each of the $\vec{\lambda}$ values can be helpful here. 
Additionally, computation of the overall variance of TI requires the calculation of the overall variance of integration, rather than each individual $\Delta$G$_{i,i+1}$ and assuming variances add independently. 
Therefore, $\mathrm{var}$($\Delta$f) = $\sum_{i=1}^{K}w_{k}^2 \mathrm{var}(\frac{du}{d\vec{\lambda}})_{k}$.
For alchemical changes that result in smooth, low curvature sets of $\expect{\frac{dU}{d\vec{\lambda}}}$, a relatively small number of $\vec{\lambda}$ states is necessary for sufficient accuracy and low variance in the free energy estimate. 
However, with increasing numbers of perturbed atoms, the bias introduced by discretization of the integral can become large due to increased curvature, and more $\vec{\lambda}$ intermediate states become necessary to reduce error.
It is recommended that researchers verify that a sufficient number of states are included such that the free energy is essentially invariant to the number of lambda intermediate states chosen.
Compared with TI, the MBAR method (section~\ref{subsec:estimators}) discussed above provides uncertainty estimation directly from solving a set of linear equations to compute the variances between all states. 
The number of states and amount of sampling should be optimized to minimize the uncertainty in the MBAR free energy estimate, while balancing other key considerations such as computational expense. 
In some cases, several analysis methods can be employed to analyze the same set of simulations, providing an opportunity for synergy. Specifically, agreement in the free energy across different estimators can be compared and discrepancy between estimates used to assess convergence.
For example, differences between free energy estimates computed with BAR, MBAR, and TI correlated with larger errors in a set of MCL1 inhibitors.
Those perturbations where free energies across different estimators shared high agreement with each other (variance less than 0.1 kcal/mol) had a r$^2$ of 0.623 and mean unsigned error (MUE) of 0.787 kcal/mol (N=17) compared with a r$^2$ of 0.295 and MUE of 1.49 kcal/mol (N=23) (unpublished results).
Uncertainty can also be assessed for a particular perturbation by repeating calculations with slight changes in initial configurations, forcefield parameters, and different random seeds in the MD engine. 
The assessment of variability in free energy calculations due to repeating simulations has been previously reported~\cite{aldeghi2019accurate,paliwal2011benchmark,mey2016blinded,mey2018impact}, and large variance in free energies estimated from simulations with different random seeds should be flagged as issues with convergence. 
Other sources that may show up as suspicious uncertainties may in fact be system set up errors. Common issues include poor ligand or protein preparation, atom mapping for relative calculations, or forcefield parameters as described above.

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig13_analysis_practices/Figure.pdf}
    \caption{\textbf{An example of recommended practices for graphing alchemical free energy predictions.} This figure shows the relation between predicted and experimentally-determined Gibbs free energy in kcal/mol with standard errors as error bars. The dark and light-orange regions depict the 1- and 2-kcal per mol confidence bounds. Extra care should be taken when investigating potential outliers further.}
    \label{fig:scatterplot_analysis}
\end{figure}

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed figures~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis},and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to introduction and drug discovery sections, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and \ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{} 4.2, 5.3, 6, 7.2.3, 8.3.1, 8.3.2, 9\\
\textbf{JDC}: Wrote section~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

>>>>

\author[2]{Hannah E. Bruce Macdonald}

@@

Although the Zwanzig equation is formally correct (as long as the two states considered sample the same phase space volume, which is true for standard molecular models), it has some very important numerical issues that mean that it often performs badly for standard free energy calculations, even for small molecules~\cite{shirts2005comparison,lu2003appropriate}.  One can show that if the standard deviation of the difference $\Delta U(\vec{q}) = U_1(vec{q})-U_2(\vec{q})$ over all sampled $\vec{q}$ is large (which in this case, means only several times $k_BT)$, then very few samples contribute to the average, and the answer will be both biased and extremely noisy~\cite{lelievre2010free}. Essentially, the method is dominated by contributions of rare snapshots\cite{jarzynski2006rare, wu2005phasespaceb, wu2005phasespacec}.

\paragraph{The Bennett Acceptance Ratio (BAR)}
If we have the differences in the potential energy sampled from the distribution defined by $U_0$ to the state defined by $U_1$, and we also have the differences in potential energies from the distribution sampled by $U_1$ to the state defined by $U_0$, we can obtain a significantly improved estimate of the
free energy difference compared to that obtained by EXP. 
This estimate was first derived by Bennett and is hence generally called the Bennett Acceptance Ratio (BAR).  It is solved by finding the reduced free energy $f_{ij}$ that satisfied the following implicit equation:
\begin{eqnarray}
 \sum_{i=1}^{n_i} \frac{1}{1 + \exp[\ln(\frac{n_i}{n_j}) + u_{ij}(\vec{q}) - f_{ij})
 ]} \nonumber \\
 =\sum_{i=1}^{n_j} \frac{1}{1 + \exp[\ln(\frac{n_i}{n_j}) - U_{ij}(\vec{q}) + f_ij)]},
\end{eqnarray}
where $n_i$ and $n_j$ are the number of samples from each state. We
will refer to this method as BAR. More recent derivations show that this formula is the maximum likelihood estimate of the free energy difference given sets of samples from the two states~\cite{shirts2003equilibriuma}.

Many studies have demonstrated both the theoretical and practical superiority of BAR over EXP in molecular
simulations~\cite{shirts2005comparison,lu2003appropriate}, and BAR converges to EXP in the limit that all samples are from a single state~\cite{bennett1976efficient,bennett1976efficient,shirts2003equilibriuma}. BAR also requires significantly less overlap between the configurational space of each state to converge than EXP, though some overlap must still exist.

@@

\paragraph{Thermodynamic integration (TI)}
By taking the derivative of the free energy with respect to the
variable $\vec{\lambda}$, we find that:
\begin{equation}
\frac{df}{d\vec{\lambda}} = \frac{d}{d\vec{\lambda}} \left[-\ln \int \frac{\exp{-u(\vec{\lambda},\vec{q})}}{Q(\vec{\lambda})} d\vec{q}\right] = \expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}\
}_{\vec{\lambda}} 
\end{equation}
And than we can then numerically integrate $df/d\vec{\lambda}$ over an alchemical transformation, using a range of different well-established techniques, to obtain:
\begin{equation}
\Delta f    = \int_{0}^{1} \expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}}_{\vec{\lambda}}  d\vec{\lambda}    
\end{equation}
This approach to calculating the free energy is called thermodynamic integration (TI). Averaging over $\expect{\frac{du}{d\vec{\lambda}}}$ requires fewer uncorrelated samples to reach a given level of relative error
than averaging $e^{-u(\vec{q})}$, as the range is usually narrower with a more Gaussian distribution. Rather than being limited by overlap, as in the case of BAR and MBAR (see below), we are instead limited by the bias in the numerical quadrature, which must be minimized sufficiently to be beneath the level of statistical noise.

Various numerical integration schemes are possible, but the trapezoid
rule provides a simple and robust scheme.  All types of numerical integration can be written as:
\[ \Delta f \approx \sum_{k=1}^{K} w_k
\expect{\frac{du(\vec{\lambda},\vec{q})}{d\vec{\lambda}}}_{k} \] where the weights $w_k$ correspond to a particular choice of numerical integration.
Researchers have tried a large number of different integration schemes~\cite{resat1993studies,jorge2010effect,shyu2009reducing}. However, many other integration choices require specific choices of $\vec{\lambda}$ to minimize bias, which makes them unsuitable when the intermediates
have widely-varying levels of uncertainty. For example, integrating a cubic spline interpolation provided negligible benefits~\cite{paliwal2011benchmark}. For starting researchers, we therefore recommend a simple trapezoid rule scheme, as it allows for maximal flexibility in which values of $\vec{\lambda}$ are simulated.  Because fitting to higher order polynomials can have numerical instabilities for some energy functions, and because alternate functional forms might only be appropriate with some types of transformations, expertise and experience is required to perform such numerical integration modifications. In practice, adding 2-3 more intermediate states is typically sufficient to match the performance of these more complicated numerical quadrature schemes.

@@

\paragraph{The multistate Bennett acceptance ratio (MBAR)}
One can generalize Bennett's logic from two states to multiple states to obtain a free energy estimator that uses energy differences between all intermediate states. MBAR gives a system of implicit equations for the free energies $f_i$:
\begin{equation}
f_i = - \ln \sum_{n=1}^{N} \frac{\exp(-u_i(\vec{q}_n))}{\sum_{k=1}^K N_k \exp(f_k-u_k(\vec{q}_n))}
\end{equation}
where there are $N_k$ samples from each of $K$ states, with $\sum_k N_k=N$ the total number of samples. Thus, we need to evaluate the energy function $U_i$ for all samples obtained at all states in the transformation. The equations can be solved by a number of different standard routines. We note that there are only $K-1$ independent equations, so only K-1 of the free energies are independent variables, and one of the $f_i$ must be specified (usually, without loss of generality, setting it to zero).

@@

\paragraph{Recommendations}
\begin{itemize}
\item We recommend MBAR if all energy differences are available. It is probably the lowest variance free energy estimate given samples from multiple states.
\item BAR is essentially just as good as MBAR for highly optimized $\vec{\lambda}$ intermediates. Specifically, if the $\vec{\lambda}$s are chosen such that intermediate states have moderate overlap with their neighbors (i.e. between $i$ and $i+1$ and between $i$ and $i-1$, they will \textit{not} have significant overlap with their next nearest neighbors $i+2$ and $i-2$. Thus MBAR does not actually get significant information from these energy differences, so one might as well not even calculate them, and just perform BAR between nearest neighbors.~\cite{paliwal2011benchmark} 
\item TI usually gives similar values as MBAR implemented with sufficient numbers of intermediates, but quadrature errors are hard to estimate beforehand.~\cite{paliwal2011benchmark}
\item WHAM is an approximation to MBAR, and there are no compelling reasons it should be used. 
\item Other variants, especially ones that adaptively determine the free energies can be  useful in certain circumstances but beyond the scope of a Best Practices article.
\end{itemize}

\subsection{Uncertainty estimation}
\label{subsec:uncertainty}
It is important to consider the variation in your computed free energies from your equilibrium simulations, in order  to  obtain an estimate of  uncertainty of the obtained value for the free energies of interest. A recent best practices paper by Grossfield et. al~\cite{grossfield2018best} provides substantial detail on how to estimate uncertainties from molecular simulations and is a good starting point for this topic. 
In general the quantification of different error metrics depends on both data generation and analysis methods  used from the ones discussed above.

The computation of free energies using TI (section~\ref{subsec:estimators}) is straightforward and the trapezoidal rule is often recommended since it allows unequal spacing of $\vec{\lambda}$ states, which is required to minimize the variance in the free energy estimate, but in principle any good numerical integration method can be used. 
The determination of regions of high curvature when estimating the integral is helpful to determine regions of phase space where more sampling and/or more $\vec{\lambda}$ states are necessary to obtain the best approximation of the integral. Generally a plot of $\vec{\lambda}$ with respect to the gradients at each of the $\vec{\lambda}$ values can be helpful here. 
Additionally, computation of the overall variance of TI requires the calculation of the overall variance of integration, rather than each individual $\Delta$G$_{i,i+1}$ and assuming variances add independently. 
Therefore, $\mathrm{var}$($\Delta$f) = $\sum_{i=1}^{K}w_{k}^2 \mathrm{var}(\frac{du}{d\vec{\lambda}})_{k}$.

For alchemical changes that result in smooth, low curvature sets of $\expect{\frac{dU}{d\vec{\lambda}}}$, a relatively small number of $\vec{\lambda}$ states is necessary for sufficient accuracy and low variance in the free energy estimate. 
However, with increasing numbers of perturbed atoms, the bias introduced by discretization of the integral can become large due to increased curvature, and more $\vec{\lambda}$ intermediate states become necessary to reduce error.
It is recommended that researchers verify that a sufficient number of states are included such that the free energy is essentially invariant to the number of lambda intermediate states chosen.

Compared with TI, the MBAR method (section~\ref{subsec:estimators}) discussed above provides uncertainty estimation directly from solving a set of linear equations to compute the variances between all states. 
The number of states and amount of sampling should be optimized to minimize the uncertainty in the MBAR free energy estimate, while balancing other key considerations such as computational expense.

In some cases, several analysis methods can be employed to analyze the same set of simulations, providing an opportunity for synergy. Specifically, agreement in the free energy across different estimators can be compared and discrepancy between estimates used to assess convergence.
For example, differences between free energy estimates computed with BAR, MBAR, and TI correlated with larger errors in a set of MCL1 inhibitors.
Those perturbations where free energies across different estimators shared high agreement with each other (variance less than 0.1 kcal/mol) had a r$^2$ of 0.623 and mean unsigned error (MUE) of 0.787 kcal/mol (N=17) compared with a r$^2$ of 0.295 and MUE of 1.49 kcal/mol (N=23) (unpublished results).

Uncertainty can also be assessed for a particular perturbation by repeating calculations with slight changes in initial configurations, forcefield parameters, and different random seeds in the MD engine. 
The assessment of variability in free energy calculations due to repeating simulations has been previously reported~\cite{aldeghi2019accurate,paliwal2011benchmark,mey2016blinded,mey2018impact}, and large variance in free energies estimated from simulations with different random seeds should be flagged as issues with convergence. 
Other sources that may show up as suspicious uncertainties may in fact be system set up errors. Common issues include poor ligand or protein preparation, atom mapping for relative calculations, or forcefield parameters as described above.

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig13_analysis_practices/FigureHBMedit.png}
    \caption{\textbf{An example of recommended practices for graphing alchemical free energy predictions.} This figure shows the relation between predicted and experimentally-determined Gibbs free energy in kcal/mol with standard errors as error bars. The dark and light-orange regions depict the 1- and 2-kcal per mol confidence bounds. Extra care should be taken when investigating potential outliers further.}
    \label{fig:scatterplot_analysis}
\end{figure}

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed figures~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis},and created figures \ref{fig:fig_what_is_lambda},~\ref{fig:fig1_what_is_alchemy},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} and improved ~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: created figures \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, the data representation section, the checklist and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to the Data Analysis section, provided the data for figure~\ref{fig:overlap} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to introduction and drug discovery sections, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and \ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote sections describing choices for alchemical pathways and analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to sections~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{} 4.2, 5.3, 6, 7.2.3, 8.3.1, 8.3.2, 9\\
\textbf{JDC}: Wrote section~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed section~\ref{subsec:accuracy}, to section~\ref{sec:relative-fe-protocol}, and to section~\ref{sec:are-they-good}.\\
\textbf{HBM} Contributed to section \ref{sec:plot_data}and Figure \ref{fig:scatterplot_analysis}.\\
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
